### 2021-11-13 NSF2021/Description/specificaim3.tex
cleaned up gantt chart

\subsubsection{Dynamics of a pair of Janus particles in ionic
solutions\label{subsubsec:JP_electrolyte}}
We propose to investigate the effects of ion transport and distribution
on the self-assembly of Janus particles within the HAP framework as
follows. First the Stokes equations are modified to incorporate the
transport of ions as
\begin{equation}
\label{eq:EKstokes}
\begin{aligned}
  &-\Delta \mathbf{u} + \nabla p = \Delta\psi\cdot\nabla\psi, \qquad
  \nabla \cdot \mathbf{u} = 0,  \quad \mathbf{x} \in \Omega,\\
  &\delta^2\Delta\psi = -\frac{1}{2}\left(n_+-n_-\right),\qquad
  \frac{\partial n_{\pm}}{\partial t} + \nabla\cdot{\bf j}_{\pm} = 0,\qquad {\bf j}_{\pm} = -\nabla n_{\pm} \mp n_{\pm} \nabla\psi + \mbox{Pe} n_{\pm}\mathbf{u},
\end{aligned}
\end{equation}
where $\psi$ is the electric potential, $\delta$ is the ratio of Debye
screening length (inversely proportional to the square root of ion
concentration) to the particle size, $\mbox{Pe}$ is the Peclet number, a
ratio between the convection and thermal diffusion time scales, and
$n_{+}$ ($n_{-}$) is the concentration of cation (anion). In the limit
of small $\delta$, PI Young and collaborator Y.~Mori (U Penn) used
asymptotic analyses to show that the jump in electric potential across
the interface (zeta potential on the Janus particle surface) may give
rise to different physical consequences such as
electrophoresis~\cite{Mori2018_JFM}.
%
An important question to address is: {\it How would such electrophoresis
be affected by the HAP between two Janus particles?} As the first part
of Specific Aim 3, we will address this important question. Results from
this effort will help elucidate the effects of salt concentration on the
assembly of Janus particles (\S\ref{subsubsec:em_effects}).

@@

\subsubsection{Electromechanical effects on the dynamic assembly of Janus particles \label{subsubsec:em_effects}}
Results from the proposed work in \S\ref{subsubsec:JP_electrolyte} will
shed light on how the electrokinetics described in~\eqref{eq:EKstokes}
may be simplified to a dielectric-like model where the bulk charges are
constant, and the fluid flow and particle mobility are determined by the
surface charge and the zeta potential as shown in~\cite{Mori2018_JFM}.
Under such simplification, equation~\eqref{eq:EKstokes} may be
re-formulated into integral forms. PIs Ryham and Young will conduct the
asymptotic analyses to derive this form, and work with PI Quaife to
design numerical algorithms to simulate the modified system. We will
first investigate the effects of salt concentration on the assembly of
Janus particles to form helices, as shown in
Figure~\ref{fig:helices_of_JPs}.

@@

Once the effects of lipid charges on the moduli are verified, the PIs
propose to examine how to use an external electric field to control the
amphiphilic self-assembly in solvent. PI Young has a track record of
working on electrohydrodynamics of an elastic, inextensible membrane
using both asymptotic analysis~\cite{Nganguia2013_PRE, Young2014_JFM,
Young2015_PoF} and numerical simulations~\cite{Nganguia2015_CiCP} and
will work with both PIs Ryham and Quaife to extend the HAP model to
study the electromechanical effects on the assembly of colloidal amphiphiles.
Results from this research will yield a quantitative understanding of
how to utilize an electric field to achieve optimal control of assembly
of amphiphiles in solvent.

>>>>

\subsubsection{Dynamics of a pair of Janus particles in ionic
solutions\label{subsubsec:JP_electrolyte}}
We propose to investigate the effects of ion transport and distribution
on the self-assembly of Janus particles within the HAP framework as
follows. First the Stokes equations are modified to incorporate the
transport of ions as
\begin{equation}
\label{eq:EKstokes}
\begin{aligned}
  &-\Delta \mathbf{u} + \nabla p = \Delta\psi\cdot\nabla\psi, \qquad
  \nabla \cdot \mathbf{u} = 0,  \quad \mathbf{x} \in \Omega,\\
  &\delta^2\Delta\psi = -\frac{1}{2}\left(n_+-n_-\right),\qquad
  \frac{\partial n_{\pm}}{\partial t} + \nabla\cdot{\bf j}_{\pm} = 0,\qquad {\bf j}_{\pm} = -\nabla n_{\pm} \mp n_{\pm} \nabla\psi + \mbox{Pe} n_{\pm}\mathbf{u},
\end{aligned}
\end{equation}
where $\psi$ is the electric potential, $\delta$ is the ratio of Debye
screening length (inversely proportional to the square root of ion
concentration) to the particle size, $\mbox{Pe}$ is the Peclet number, a
ratio between the convection and thermal diffusion time scales, and
$n_{+}$ ($n_{-}$) is the concentration of cation (anion). In the limit
of small $\delta$, PI YNY and collaborator Y.~Mori (U Penn) used
asymptotic analyses to show that the jump in electric potential across
the interface (zeta potential on the Janus particle surface) may give
rise to different physical consequences such as
electrophoresis~\cite{Mori2018_JFM}.
%
An important question to address is: {\it How would such electrophoresis
be affected by the HAP between two Janus particles?} As the first part
of Specific Aim 3, we will address this important question. Results from
this effort will help elucidate the effects of salt concentration on the
assembly of Janus particles (\S\ref{subsubsec:em_effects}).

@@

\subsubsection{Electromechanical effects on the dynamic assembly of Janus particles \label{subsubsec:em_effects}}
Results from the proposed work in \S\ref{subsubsec:JP_electrolyte} will
shed light on how the electrokinetics described in~\eqref{eq:EKstokes}
may be simplified to a dielectric-like model where the bulk charges are
constant, and the fluid flow and particle mobility are determined by the
surface charge and the zeta potential as shown in~\cite{Mori2018_JFM}.
Under such simplification, equation~\eqref{eq:EKstokes} may be
re-formulated into integral forms. PIs RR and YNY will conduct the
asymptotic analyses to derive this form, and work with PI BQ to design
numerical algorithms to simulate the modified system. We will first
investigate the effects of salt concentration on the assembly of Janus
particles to form helices, as shown in Figure~\ref{fig:helices_of_JPs}.

@@

Once the effects of lipid charges on the moduli are verified, the PIs
propose to examine how to use an external electric field to control the
amphiphilic self-assembly in solvent. PI YNY has a track record of
working on electrohydrodynamics of an elastic, inextensible membrane
using both asymptotic analysis~\cite{Nganguia2013_PRE, Young2014_JFM,
Young2015_PoF} and numerical simulations~\cite{Nganguia2015_CiCP} and
will work with both PIs RR and BQ to extend the HAP model to study the
electromechanical effects on the assembly of colloidal amphiphiles.
Results from this research will yield a quantitative understanding of
how to utilize an electric field to achieve optimal control of assembly
of amphiphiles in solvent.
